\cvsection{Experience}

\begin{cventries}
  \cventry
    {Sr. Software Engineer} % Job title
    {Transport4} % Organization
    {Atlanta, GA} % Location
    {Apr. 2020 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Construct serverless APIs on AWS using Node \& Typescript}
        \item {Mentor and train new team members}
        \item {Design DynamoDB (NoSQL) data model}
        \item {Create deployment pipeline via GitHub Actions}
        \item {Elasticsearch modeling and schema design optimization}
      \end{cvitems}
    }
    
  \cventry
    {Software Engineer} % Job title
    {Delta Airlines} % Organization
    {Atlanta, GA} % Location
    {Nov. 2019 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design \& implement a serverless data pipeline migrating exisiting on-prem processes to AWS}
        \item {Convert existing code base from Spark/Scala to Python}
        \item {Mentor peers on AWS Best Practices \& Python development}
        \item {Develop CI/CD Pipelines on AWS converting on-prem pipelines completely serverless}
      \end{cvitems}
    }

  \cventry
    {Software Engineer II} % Job title
    {Cox Automotive} % Organization
    {Atlanta, GA} % Location
    {Jan. 2019 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Create an event-driven serverless service-oriented architecture (SOA) entirely on AWS}
        \item {Design \& maintain RESTful API endpoints using API Gateway, AWS Lambda \& AWS Elasticsearch Service}
        \item {Stream data from auctions across the country using AWS Kinesis}
        \item {Mentor \& train junior developers on AWS \& Python}
        \item {Reduce Lambda execution time by 70\% by implementing best practices leading to a latency reduction by 10\%}
        \item {Convert existing Angular code base to React implementing a component-based architecture}
      \end{cvitems}
    }

  \cventry
    {Software Engineer I} % Job title
    {Cox Automotive} % Organization
    {Atlanta, GA} % Location
    {Jan. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Black box testing for our React front-end.}
        \item {Build \& maintain RESTful API endpoints using the Java Spring Framework}
        \item {Transition legacy FTP processes using S3 and AWS Lambda}
      \end{cvitems}
    }
    
  \cventry
    {Software Engineer in Test} % Job title
    {Cox Automotive} % Organization
    {Atlanta, GA} % Location
    {May. 2016 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Translate business requirements into automatable scenarios (Gherkin)}
        \item {Data validation of critical production reports using PostgreSQL and PL/pgSQL}
        \item {API test automation using Ruby and the Cucumber framework}
      \end{cvitems}
    }
\end{cventries}
